The Shape Matching Element Method: Direct Animation of Curved Surface Models

### 2021-01-28 paper/sections/methods.tex
update distance weight plot

\begin{figure}[h]
    \centering
    \includegraphics[width=3.33in]{figures/plot_distance_weight.pdf}
    \caption{Distance weight as a function of primary and total ray length with cutoff distance 50.}
    % \caption{We plot the distance weight with respect to the primary and total ray length. Here the cutoff distance is 50.
    % }
    \label{fig:plot_distance_weight}
    \vspace{-5pt}
\end{figure}

Using these two distances we define a linear \emph{distance weight} using the well-known ReLU function:
\begin{equation}
\theta_i = \max \left(1.0 - \frac{d_{\text{primary}}}{\min (d_{\text{total}}, \alpha)}, 0.0\right)
\text{,}
\end{equation}
where $\alpha$ is a distance cutoff parameter. 
This distance weight~(\reffig{plot_distance_weight}) is the result of interpolating along the ray from $\clst$ to $\rhit$ (or a fixed point that depends on $\alpha$). 
These weights obey the Kronecker delta property for all parts but do not partition unity which we repair using a post-normalization step. For non-planar surfaces, $\rhit$ may lie on the same part as $\clst$. For points inside closed periodic surfaces, it is critical that the weights equal one in this case, so we set $\theta_i = 1$.

>>>>

\begin{figure}[h]
    \centering
    \includegraphics[width=3.33in]{figures/plot_distance_weight_both.pdf}
    \caption{Distance weight as a function of primary and total ray length with cutoff distance 50 (left). Here we use different colors to denote different parts (right).}
    % \caption{We plot the distance weight with respect to the primary and total ray length. Here the cutoff distance is 50.
    % }
    \label{fig:plot_distance_weight}
    \vspace{-5pt}
\end{figure}

Using these two distances we define a linear \emph{distance weight} using the well-known ReLU function:
\begin{equation}
\theta_i = \max \left(1.0 - \frac{d_{\text{primary}}}{\min (d_{\text{total}}, \alpha)}, 0.0\right)
\text{,}
\end{equation}
where $\alpha$ is a distance cutoff parameter, $d_{\text{primary}}$ is the primary ray length and $d_{\text{total}}$ is the total ray length. 
This distance weight~(\reffig{plot_distance_weight}) is the result of interpolating along the ray from $\clst$ to $\rhit$ (or a fixed point that depends on $\alpha$). 
These weights obey the Kronecker delta property for all parts but do not partition unity which we repair using a post-normalization step. For non-planar surfaces, $\rhit$ may lie on the same part as $\clst$. For points inside closed periodic surfaces, it is critical that the weights equal one in this case, so we set $\theta_i = 1$.
